### 2017-08-01 Paper01_EnthalpyAndCrystallization.tex
Figures - Added deconvolution figures in a 3x3 grid

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 108.5 & 128.6 &  & 177.3 &  & 240.3 \\
		80  & 106.0 & 121.2 &  & 165.6 &  & 238.8 \\
		60  & 107.3 & 134.0 &  & 176.1 &  & 237.8 \\
		40  & 100.2 & 119.8 &  & 170.7 &  & 234.2 \\
		30  & 95.3  & 110.4 &  & 169.5 &  & 232.5 \\
		20  & 95.5  & 115.2 &  & 170.5 &  & 229.4 \\
		15  & 92.5  & 113.5 &  & 168.8 &  & 224.0 \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
	\label{tab:DSCOnsets}
\end{table}

@@

Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system. Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ [source] for both the bulk and film. The fragility $m$ could then be calcuated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].

@@

@@

The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher. This higher heating rates were used because crystallization events for the films were different to differentiation at the lower heating rate. 
Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.

>>>>

Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates to observe changed in the \Tg and \Tx temperatures. As expected higher heating rates resulted endothermic peaks shifting to higher temperatures and curve convolution.

Numerical solutions were used to deconvolution the \acrshort{dsc} data so the various \Tx onsets could be determined. The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 108.5 & 128.6 &  & 177.3 &  & 240.3 \\
		80  & 106.0 & 121.2 &  & 165.6 &  & 238.8 \\
		60  & 107.3 & 134.0 &  & 176.1 &  & 237.8 \\
		40  & 100.2 & 119.8 &  & 170.7 &  & 234.2 \\
		30  & 95.3  & 110.4 &  & 169.5 &  & 232.5 \\
		20  & 95.5  & 115.2 &  & 170.5 &  & 229.4 \\
		15  & 92.5  & 113.5 &  & 168.8 &  & 224.0 \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
	\label{tab:FilmOnsets}
\end{table}

@@

Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system. Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ [source] for both the bulk and film. The fragility $m$ could then be calculated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].

@@

%MultiFigure
\begin{figure}[b]
	\centering
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_5Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_10Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_15Ks_result_A5lsc.png}

	\medskip

	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_20Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_30Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_40Ks_result_A5lsc.png}

	\medskip

	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_60Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_80Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}

	\caption{\acrshort{dsc} deconvolution for the bulk. From left to right, top to bottom, 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
	\label{fig:DSC_Bulk_Decon}
\end{figure}

%MultiFigure
\begin{figure}[b]
	\centering
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_15Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_20Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_30Ks_result_A5lsc.png}

	\medskip

	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_40Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_60Ks_result_A5lsc.png}\quad
	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_80Ks_result_A5lsc.png}

	\medskip

	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}

	\caption{\acrshort{dsc} deconvolution for the film. From left to right, top to bottom, 15, 20, 30, 40, 60, 80, 100 K/min.}
	\label{fig:DSC_Film_Decon}
\end{figure}

@@

The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher. This higher heating rates were used because crystallization events for the films were difficult to differentiation at the lower heating rate. 
Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.
